D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-21 ootavacuous.tex
Alan Stern February 21 feedback, Section 8
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Real-world constraints are imposed by the standard, which have been
considered in prior work.
However, in correct real-world C++ implementations, the standard's
abstract machine must be mapped onto real matter and energy.
This mapping has not been considered by prior work, and brings to
bear additional constraints from the laws of physics and from hardware
architecture and design, both of which have been only partially accounted
for in the standard and in prior work.
One reason for the incomplete accounting for hardware constraints is
that accurate and executable formal descriptions of hardware memory
models did not appear until after the standard was released.
A final set of constraints is imposed by the C++ implementations
themselves, some of which have resulted in nondeterminisms within
the standard.\footnote{
	For example, when pre-existing implementations could not agree
	on any specific deterministic handling of side-effects within
	expressions.
	On the other hand, implementer freedom does have significant
	value.}

The following sections discuss these constraints, starting with
with hardware constraints, continuing
further with constraints imposed by the standard, and culminating
with constraints imposed by the C++ implementations themselves.
An additional section discusses the OOTA-cycle implications for
any tooling that exists separately for these C++ implementations.

>>>>

The C++ standard imposes many constraints, and these have been considered
in prior work.
However, in correct real-world C++ implementations, the standard's
abstract machine must be mapped onto real matter and energy.
This mapping has not been considered by prior work, and brings to
bear additional constraints from from hardware architecture and
design,\footnote{
	Which is in turn constrained by the laws of physics.}
which has been only partially accounted for in the standard and in
prior work.
One reason for the incomplete accounting for hardware constraints is
that accurate and executable formal descriptions of hardware memory
models did not appear until after the standard was released.

The following sections discuss these constraints, starting with with
hardware constraints and continuing with additional constraints imposed
by the standard.
An additional section discusses the OOTA-cycle implications for C++
tooling.
